### 2018-10-05 papers/journal/related.tex
Related section SAT/SMT part rewrite

Modern day SAT/SMT solvers can handle millions of variables and due to the exhaustive nature of the searching, solving the combinatorial problem is a natural fit for the SAT/SMT solvers. There are many graphs related combinatorial work \cite{gay2013solving,wotzlaw2012generalized} that have used SAT solvers. Thanks to the improvement in SAT solver and formal techniques, tools like model checkers and theorem provers scalability and combinatorial solving capability are now being used to model complex biological systems \cite{heule2010exact,yordanov2013smt,mangla2010timing}.
% Many network questions are being reduced to solving a SAT question.
Many of these biological system uses these tools and techniques to reason about graphs and networks rules with possible exhaustive search \cite{guerra2012reasoning,chin2008biographe}.

Recently these tools and techniques have found the use of modeling and understanding the gene regulatory networks (GNR) \cite{giacobbe2015model,rosenblueth2014inference, batt2010efficient, yordanov2016method, dunn2014defining, paoletti2014analyzing, koksal2013synthesis}. GNR is a complex system driven by many complex rules. We extended this work and have applied model checkers to the more complex transport network (VTS) \cite{mani2016stacking,shukla}, but scaling it to cases which are interesting biologically is still a challenge. In this paper, we have achieved the scalability required for analyzing VTS for eukaryotic cells, of total ten compartments (N = 10). \\

>>>>

SAT and SMT solvers are a perfect fit for solving combinatorial problems due to their exhaustive nature of searching. 
%
Improvement in SAT and SMT solvers in the past decades have led to their use in modeling and understanding complex biological systems~\cite{heule2010exact,yordanov2013smt,mangla2010timing}. 
%
Many of which involve reasoning about graphs and networks rules with possible exhaustive search and hence can be reduced to solving a SAT/SMT question. 
%
Modeling and understanding the gene regulatory networks (GNR)~\cite{guerra2012reasoning,chin2008biographe}, modeling and understanding the gene regulatory networks (GNR) \cite{giacobbe2015model,rosenblueth2014inference, batt2010efficient, yordanov2016method, dunn2014defining, paoletti2014analyzing, koksal2013synthesis} is one such example. 
%
We have extended the application of SAT and SMT solvers to the most comple Biological transport network (VTS) \cite{mani2016stacking,shukla}.
